Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-12 providence/sections/adversary.tex
Update adversary.tex

To illustrate the practical implication of this property, we consider a toy example: an RLA of a two-candidate contest with margin $1\%$ and risk limit $10\%$. 
Suppose we wish to achieve a conditional stopping probability $0.9$ in each round of the audit. For \Providence, we can compute a new round size for each round based on the previous samples. For \Minerva, however, we would have a predetermined round schedule. We use the default \Minerva round schedule of audit software Arlo \cite{arlo} (used by most states performing an RLA), which is is $[x, 2.5x, 6.25x, ...]$; that is, the next marginal round size is $1.5$ times the current one. This multiplier of $1.5$ is known to give, over a wide range of margins, a probability of stopping roughly $0.9$ in the second round if the first round size has probability of stopping $0.9$.

@@

\subsection{Efficiency}
\begin{lemma}
% For any round schedule %$[n_1, \ldots, n_r]$
For any risk-limit $\alpha \in (0, 1)$, for any margin
and for any round schedule $[n_1, \ldots, n_j]$, 
the \Providence RLA is more efficient than EoR \BRAVO.
\end{lemma}
\begin{proof}
Let $[n_1, \ldots, n_j]$ be a round schedule, and assume that an EoR \BRAVO audit stops in round $j$, after observing $k_1, \ldots, k_j$ ballots for the announced winner in each round respectively.
That is, the EoR \BRAVO stopping condition is true:
$$\sigma(k_j,p_a,p_0,n_j) \ge \frac{1}{\alpha}.$$
To see the the \Providence stopping condition is fulfilled, we rewrite as 
%$$\frac{1}{\alpha} \le \sigma(k_j,p_a,p_0,n_j)=\sigma(k_j,p_a,p_0,n_j)$$

@@

Where inequality $(*)$ follows from \cite[Theorem 6]{athena}.
%Where inequality $(*)$ follows from Lemma~\ref{lemma:frac_sums_increasing}.
%the well-known property that if $a_i/b_i$ (for $a_i, b_i > 0$) is monotonicly increasing then
%(\sum_{i} a_i)/(\sum_{i} b_i)$ is also monotonicly increasing.

>>>>

To illustrate the practical implication of this property, we consider a toy example: an RLA of a two-candidate contest with margin $0.01$ and risk limit $0.1$. 
Suppose we wish to achieve a conditional stopping probability $0.9$ in each round of the audit. For \Providence, we can compute a new round size for each round based on the previous samples. For \Minerva, however, we would have a predetermined round schedule. We use the default \Minerva round schedule of audit software Arlo \cite{arlo} (used by most states performing an RLA), which is is $[x, 2.5x, 6.25x, ...]$; that is, the next marginal round size is $1.5$ times the current one. This multiplier of $1.5$ is known to give, over a wide range of margins, a probability of stopping roughly $0.9$ in the second round if the first round size has probability of stopping $0.9$.

@@

\subsection{Efficiency}
\begin{lemma}
% For any round schedule %$[n_1, \ldots, n_r]$
For any risk-limit $\alpha \in (0, 1)$, for any margin
and for any round schedule $[n_1, \ldots, n_j]$, 
the \Providence RLA is more efficient than EoR \BRAVO.
\end{lemma}
\begin{proof}
Let $[n_1, \ldots, n_j]$ be a round schedule, and assume that an EoR \BRAVO audit stops in round $j$, after observing $k_1, \ldots, k_j$ ballots for the announced winner in each round respectively.
That is, the EoR \BRAVO stopping condition is true:
$$\sigma(k_j,p_a,p_0,n_j) \ge \frac{1}{\alpha}.$$
To see the \Providence stopping condition is fulfilled, we rewrite as 
%$$\frac{1}{\alpha} \le \sigma(k_j,p_a,p_0,n_j)=\sigma(k_j,p_a,p_0,n_j)$$

@@

Where inequality $(*)$ follows from \cite[Theorem 6]{athena}. Note that we apply this result on $\tau_j$ for just $j=1$.
%Where inequality $(*)$ follows from Lemma~\ref{lemma:frac_sums_increasing}.
%the well-known property that if $a_i/b_i$ (for $a_i, b_i > 0$) is monotonicly increasing then
%(\sum_{i} a_i)/(\sum_{i} b_i)$ is also monotonicly increasing.
